Commutative Character Sheaves

### 2015-09-18 followup.tex
Added todo

We now suppose that $H$ is normal in $G$, that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.

@@

By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
This exists in schemes since  . . . 
%\todo{Proof needed}
%  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
\[
\begin{tikzcd}
G\der\times G
 \arrow{r}[shift left]{n}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]

@@

\begin{proof}
The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$.} so the result follows from Lemma~\ref{lem:descent}.
\end{proof}

@@

 \begin{proof}
 By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
By Theorem~\ref{thm:Gab-descent}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
Since $G\der$ is simply connected,\todo{Proof needed}, $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
Thus, all characters of $G(\Fq)$ factor through
 $G\ab(\Fq)$. . . . 
 The isomorphisms are compatible because  . . . 
 \end{proof}

>>>>

We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.

@@

By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
This exists in schemes since  . . . \todo{I hope smoothness does the trick here.}
%\todo{Proof needed}
%  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
\[
\begin{tikzcd}
G\der\times G
 \arrow{r}[shift left]{n}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G\ab
\end{tikzcd}
\]

@@

\begin{proof}
The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$. Again, I hope smoothness does the trick.} so the result follows from Lemma~\ref{lem:descent}.
\end{proof}

@@

 \begin{proof}
 By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
By Theorem~\ref{thm:Gab-descent}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
Since $G\der$ is simply connected, \todo{Proof needed} $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
Thus, all characters of $G(\Fq)$ factor through
 $G\ab(\Fq)$. . . . 
 The isomorphisms are compatible because  . . . 
 \end{proof}
